Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
tikz example for drawing dataflow graphs
fixed refs

@@

Edges in the dataflow graph represent files, the basic data
abstraction of the shell. They are used as communication channels
between nodes in the graph, and as the input or output of the whole
graph. Edges are represented as possibly unbounded streams of type
$D*$. They could either refer to a specific named file in the file
system, or just be FIFO pipes that used for interprocess communication
%% \TODO{Are there any other file types, such as URLs, ...?}.

@@

@@

In order to adequately utilize the available computational resources,
a distributed implementation should exploit data parallelism. Data
parallelism is based on the observation that some operations produce
the same result when performed independently on subsets of the input
data, merging the results afterwards. This is the basic optimization
that is used by popular distributed processing systems such as
MapReduce\kk{cite} and Apache Spark\kk{cite}.Unfortunately, the
dataflow graph model of most of these systems is not expressive enough
to represent data parallelism, so the distributed implementations that
they perform do not preserve the semantics of their dataflow model.

>>>>

\usepackage{tikz}
\usetikzlibrary{arrows,automata,shapes.misc,shapes.geometric,positioning}

@@

Edges in the dataflow graph represent files, the basic data
abstraction of the shell. They are used as communication channels
between nodes in the graph, and as the input or output of the whole
graph. Edges are represented as possibly unbounded streams of type
$D\kstar$. They could either refer to a specific named file in the file
system, or just be FIFO pipes that used for interprocess communication
%% \TODO{Are there any other file types, such as URLs, ...?}.

@@

\begin{center}
\small
\begin{tikzpicture}[node distance=2.25cm, ->]
\node (S) {};
\node (A) [draw, right of=S, node distance=1.75cm] {node 1};
\node (B) [draw, right of=A] {node 2};
\node (C) [draw, right of=B] {node 3};
\node (E) [right of=C, node distance=1.75cm] {};
\path (S) edge node[above] {input} (A);
\path (A) edge node[above] {stream} (B);
\path (B) edge node[above] {stream} (C);
\path (C) edge node[above] {output} (E);
\end{tikzpicture}
\end{center}

@@

In order to adequately utilize the available computational resources,
a distributed implementation should exploit data parallelism. Data
parallelism is based on the observation that some operations produce
the same result when performed independently on subsets of the input
data, merging the results afterwards. This is the basic optimization
that is used by popular distributed processing systems such as
MapReduce \cite{DG2004MR} and Apache Spark\cite{spark:12}. Unfortunately, the
dataflow graph model of most of these systems is not expressive enough
to represent data parallelism \km{not sure this is true}, so the distributed implementations that
they perform do not preserve the semantics of their dataflow model.
